Capstone Movielens Report

### 2025-12-15 reports/capstone-movielens.site/05.appendix.Rmd

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

#### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
\

@@

```{r eval=FALSE}
```

@@

Internally it uses the [train_UMGY_effect.cv](#func.train_UMGY_effect.cv) and [calc_UMGY_effect_RMSE.cv](#func.calc_UMGY_effect_RMSE.cv) functions described above to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).

::: {.noteblock data-latex=""}
This function is also intended to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L130) script on _GitHub_.
:::
:::

>>>>

::: {.noteblock data-latex=""}
This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

#### [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) Function {#func.regularize.test_lambda.UMGYD_effect.cv}
\

@@

```{r eval=FALSE}
UMGYDE.rglr.fine_tune.results <- 
  model.tune.param_range(UMGYDE.loop_starter,
                         UMGYDE.rglr.fine_tune.cache.path,
                         cache.base_name,
                         regularize.test_lambda.UMGYD_effect.cv)
```

::: {.noteblock data-latex=""}
In the code snippet above this function is passed in the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) argument to the [model.tune.param_range](#func.model.tune.param_range) function described above in the section *Common Helper Functions /* [Regularization Functions] of *this Appendix*.

@@

Internally it uses the [regularize.train_UMGYD_effect.cv](#func.regularize.train_UMGYD_effect.cv) (described above in this section) and [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) functions (described in section [UMGYDE Model: Utility Functions] above) to validate the *UMGYDE Model* for the given $\lambda$ with use of the *K-Fold Cross-Validation* method, as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV], where the value of $K$ is determined by the length of the [`edx_CV` Object] described below in [Appendix B: Models Training Datasets] (in *this Project* we use $K = 5$).

::: {.noteblock data-latex=""}
This function is an auxiliary function specifically designed to be passed in the `fn_tune.test.param_value` argument to the [tune.model_param](#func.tune.model_param) and [model.tune.param_range](#func.model.tune.param_range) functions described above in the *Common Helper Functions /* [Regularization Functions] section of *this Appendix*.
:::
:::

@@

The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) function is shown below:
```{r eval=FALSE}
regularize.test_lambda.UMGYD_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.UMGYD_effect.cv
`lambda` is `NA`")
  }

  regularize.train_UMGYD_effect.cv(lambda) |>
    calc_UMGY_SmoothedDay_effect.RMSE.cv()
}
```

::: {.noteblock data-latex=""}
The source code of the [regularize.test_lambda.UMGYD_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) function is also available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L224) section of the [UMGYD-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L242) script on _GitHub_.
:::
:::
